oREV item selection

### 2022-11-10 analysis/item_selection.Rmd
add omp graphs

```{r}

rasch_fit <- irt_dat%>%
  left_join(aoa)%>%
  select(-order, -sex)%>%
  filter(#targetWord %in% c("door", "jaguar","zucchini"),
         #subjID %in% c("15X7mwV1", "39tVizn3", "479FefBH")
         )%>%
  add_epred_draws(irt1_guess, re_formula = ~(1 | targetWord) + (1 | subjID), ndraws = 5000)%>%
  mutate(zvi = (correct - .epred)/(.epred*(1-.epred))^0.5)%>%
  group_by(targetWord,aoa_german_comb, .draw)%>%
  summarise(outfit = sum(zvi^2)/length(unique(subjID)),
            infit = (sum(zvi^2*(.epred*(1-.epred)))/sum(.epred*(1-.epred))))

@@

```{r}
rasch_fit%>%
  pivot_longer(names_to = "fit_index", values_to = "value", cols = c(outfit, infit))%>%
  ggplot(. , aes(y = fct_reorder(targetWord, aoa_german_comb), x = value, col = fit_index))+
  geom_vline(xintercept = c(0.7, 1.3), lty = 3, alpha = .5)+
  geom_vline(xintercept = c(0.5, 1.5), lty = 2, alpha = .5)+
  geom_vline(xintercept = 1, lty = 1, alpha = .5, col = "darkgreen")+
  stat_halfeye(alpha = .75, .width = c(0.66, 0.95), position = position_dodge())+
  scale_fill_colorblind()+
  scale_color_colorblind(name = "Fit index")+
    labs(x = "Index value", y = "Target word (sorted by rated age of acquisition)")+
  #facet_grid(~fit_index)+
  scale_x_continuous(breaks = c(0,0.5, 07, 1, 1.3, 1.5), labels = c(0,0.5, 07, 1, 1.3, 1.5), limits = c(0,7))+
  theme_bw()+
  theme(legend.position = c(0.8,0.8))
```
```{r}
ggsave("../graphs/in_outfit.png", height = 12, width = 10, scale = 1)
```

@@

```{r}
rasch_fit%>%
  filter(targetWord %in% frq_sel_items_rasch)%>%
  pivot_longer(names_to = "fit_index", values_to = "value", cols = c(outfit, infit))%>%
  ggplot(. , aes(y = fct_reorder(targetWord, aoa_german_comb), x = value, fill = fit_index, col = fit_index))+
  geom_vline(xintercept = c(0.5, 1.5), lty = 2, alpha = .5)+
  geom_vline(xintercept = c(0.7, 1.3), lty = 3, alpha = .5)+
  geom_vline(xintercept = 1, lty = 1, alpha = .5, col = "darkgreen")+
  stat_halfeye(alpha = .75, .width = c(0.66, 0.95), position = position_dodge(width = 0.5))+
  scale_fill_colorblind()+
  scale_color_colorblind()+
  labs(x = "Index value", y = "Target word (sorted by rated age of acquisition)")+
  #facet_grid(~fit_index)+
  xlim(0,3)+
  theme_bw()
```

@@

```{r}
icc1_sel <- posterior_samples(irt1_guess)%>% 
  select(b_eta_Intercept, starts_with("r_targetWord"))%>%
  mutate(iter = 1:n()) %>% 
  pivot_longer(starts_with("r_targetWord"), names_to = "item", values_to = "xi") %>%
  mutate(item = str_extract(string = item, pattern = "(?<=\\[).*(?=,Intercept\\])"))%>%
  filter(item %in% sel_items_rasch)%>%
  expand(nesting(iter, b_eta_Intercept, item, xi),
         theta = seq(from = -6, to = 6, length.out = 100)) %>% 
  mutate(p = 0.25 + 0.75*inv_logit_scaled((b_eta_Intercept + theta + xi))) %>%  
  group_by(theta, item) %>% 
  summarise(p = mean(p))%>%
  left_join(aoa%>%rename(item = targetWord))
```

@@

>>>>

```{r}
rasch_fit <- irt_dat%>%
  left_join(aoa)%>%
  select(-order, -sex)%>%
  filter(targetWord %in% rasch_selected_items,
         #subjID %in% c("15X7mwV1", "39tVizn3", "479FefBH")
         )%>%
  add_epred_draws(irt1_guess_sel, re_formula = ~(1 | targetWord) + (1 | subjID), ndraws = 5000)%>%
  mutate(zvi = (correct - .epred)/(.epred*(1-.epred))^0.5)%>%
  group_by(targetWord,aoa_german_comb, .draw)%>%
  summarise(outfit = sum(zvi^2)/length(unique(subjID)),
            infit = (sum(zvi^2*(.epred*(1-.epred)))/sum(.epred*(1-.epred))))

@@

```{r}
rasch_fit%>%
  pivot_longer(names_to = "fit_index", values_to = "value", cols = c(outfit, infit))%>%
  ggplot(. , aes(y = fct_reorder(targetWord, aoa_german_comb), x = value, col = fit_index))+
  geom_vline(xintercept = c(0.7, 1.3), lty = 3, alpha = .5)+
  geom_vline(xintercept = c(0.5, 1.5), lty = 2, alpha = .5)+
  geom_vline(xintercept = 1, lty = 1, alpha = .5, col = "darkgreen")+
  stat_halfeye(alpha = .75, .width = c(0.66, 0.95), position = position_dodge())+
  scale_fill_colorblind()+
  scale_color_colorblind(name = "Fit index")+
    labs(x = "Index value", y = "Target word (sorted by rated age of acquisition)")+
  #facet_grid(~fit_index)+
  scale_x_continuous(breaks = c(0,0.5, 07, 1, 1.3, 1.5), labels = c(0,0.5, 07, 1, 1.3, 1.5), limits = c(0,7))+
  theme_bw()+
  theme(legend.position = c(0.8,0.8))
```

```{r}
ggsave("../graphs/in_outfit.png", height = 12, width = 10, scale = 1)
```

@@

```{r}
rasch_selected_items <- readRDS("../saves/selected_items_rasch.rds")

rasch_fit_sel_guess <- irt_dat%>%
  left_join(aoa)%>%
  select(-order, -sex)%>%
  filter(targetWord %in% rasch_selected_items,
         #subjID %in% c("15X7mwV1", "39tVizn3", "479FefBH")
         )%>%
  add_epred_draws(irt1_guess_sel, re_formula = ~(1 | targetWord) + (1 | subjID), ndraws = 5000)%>%
  mutate(zvi = (correct - .epred)/(.epred*(1-.epred))^0.5)%>%
  group_by(targetWord,aoa_german_comb, .draw)%>%
  summarise(outfit = sum(zvi^2)/length(unique(subjID)),
            infit = (sum(zvi^2*(.epred*(1-.epred)))/sum(.epred*(1-.epred))))

```{r}
rasch_fit_sel_guess%>%
  filter(targetWord %in% rasch_selected_items)%>%
  pivot_longer(names_to = "fit_index", values_to = "value", cols = c(outfit, infit))%>%
  ggplot(. , aes(y = fct_reorder(targetWord, aoa_german_comb), x = value, fill = fit_index, col = fit_index))+
  geom_vline(xintercept = c(0.5, 1.5), lty = 2, alpha = .5)+
  geom_vline(xintercept = c(0.7, 1.3), lty = 3, alpha = .5)+
  geom_vline(xintercept = 1, lty = 1, alpha = .5, col = "darkgreen")+
  stat_halfeye(alpha = .75, .width = c(0.66, 0.95), position = position_dodge(width = 0.5))+
  scale_fill_colorblind()+
  scale_color_colorblind()+
  labs(x = "Index value", y = "Target word (sorted by rated age of acquisition)")+
  #facet_grid(~fit_index)+
  xlim(0,3)+
  theme_bw()
```

### Compare initial and re-fitted fir indices

```{r}
bind_rows(rasch_fit_sel_guess%>%mutate(fit = "selected items only"),
          rasch_fit%>%mutate(fit = "all items"))%>%
  filter(targetWord %in% rasch_selected_items)%>%
  pivot_longer(names_to = "fit_index", values_to = "value", cols = c(outfit, infit))%>%
  ggplot(. , aes(y = fct_reorder(targetWord, aoa_german_comb), x = value, fill = fit_index, col = fit_index, lty = fit, pch = fit))+
  geom_vline(xintercept = c(0.5, 1.5), lty = 2, alpha = .5)+
  geom_vline(xintercept = c(0.7, 1.3), lty = 3, alpha = .5)+
  geom_vline(xintercept = 1, lty = 1, alpha = .5, col = "darkgreen")+
  stat_halfeye(alpha = .75, .width = c(0.66, 0.95), position = position_dodge(width = 0.9))+
  scale_fill_colorblind()+
  scale_color_colorblind()+
  labs(x = "Index value", y = "Target word (sorted by rated age of acquisition)")+
  #facet_grid(~fit_index)+
  xlim(0,3)+
  theme_bw()
```
```{r}
ggsave("../graphs/fit_index_comp.png", height = 12, width = 10, scale = 1)
```

@@

```{r}
icc1_guess_sel <- posterior_samples(irt1_guess_sel)%>% 
  select(b_eta_Intercept, starts_with("r_targetWord"))%>%
  mutate(iter = 1:n()) %>% 
  pivot_longer(starts_with("r_targetWord"), names_to = "item", values_to = "xi") %>%
  mutate(item = str_extract(string = item, pattern = "(?<=\\[).*(?=,Intercept\\])"))%>%
  expand(nesting(iter, b_eta_Intercept, item, xi),
         theta = seq(from = -6, to = 6, length.out = 100)) %>% 
  mutate(p = 0.25 + 0.75*inv_logit_scaled((b_eta_Intercept + theta + xi))) %>%  
  group_by(theta, item) %>% 
  summarise(p = mean(p))%>%
  left_join(aoa%>%rename(item = targetWord))
```

@@

### compare 1PL and 2PL ICCs

```{r}
icc3_sel <- posterior_samples(irt3_sel)%>% 
  select(b_eta_Intercept, b_logalpha_Intercept, starts_with("r_targetWord"))%>%
  mutate(iter = 1:n()) %>% 
  pivot_longer(starts_with("r_targetWord")) %>%
  mutate(item      = str_extract(name, pattern = "(?<=\\[).*(?=,Intercept\\])"),
         parameter = ifelse(str_detect(name, "eta"), "xi", "logalpha"))%>%
  select(-name) %>% 
  pivot_wider(names_from = parameter, values_from = value)%>% 
  expand(nesting(iter, b_eta_Intercept, b_logalpha_Intercept, item, xi, logalpha),
         theta = seq(from = -6, to = 6, length.out = 100)) %>% 
  # note the difference in the equation
  mutate(p = 0.25 + 0.75*inv_logit_scaled(exp(b_logalpha_Intercept + logalpha) * (b_eta_Intercept + theta + xi))) %>% 
  group_by(theta, item) %>% 
  summarise(p = mean(p))%>%
  left_join(aoa%>%rename(item = targetWord))
```

```{r}
bind_rows(icc1_guess_sel%>%mutate(model = "1PL + guessing"),
          icc3_sel%>%mutate(model = "2PL + guessing")) %>% 
  ggplot(aes(x = theta, y = p,group = interaction(item,model), col = model)) +
  geom_line() +
  facet_wrap(~item)+
  #guides(col = F)+
  geom_hline(yintercept = 0.25, lty = 3, alpha = .75)+
  scale_color_solarized(name = "Model") +
  labs(title = "Comparing ICCs for 1PL and 2PL",
       x = expression(theta~('ability on the logit scale')),
       y = expression(italic(p)(y==1))) +
  ylim(0,1)+
  theme_minimal()
```
```{r}
ggsave("../graphs/fit_index_comp.png", height = 10, width = 14, scale = 1)
```
